\documentclass[t]{beamer}
\usetheme{Copenhagen}
\setbeamertemplate{headline}{} % remove toc from headers
\beamertemplatenavigationsymbolsempty

\usepackage{amsmath, array, tikz, bm, pgfplots, tcolorbox, graphicx, venndiagram, color, colortbl, xfrac}
\pgfplotsset{compat = 1.16}
\usepgfplotslibrary{statistics}
\usetikzlibrary{calc}

\title{Hypothesis Testing}
\subtitle{Two Sample Proportions}
\author{}
\date{}

\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Objectives}
    \tableofcontents[currentsection]
  \end{frame}
}

\begin{document}

\pgfmathdeclarefunction{gauss}{2}{%
  \pgfmathparse{1/(#2*sqrt(2*pi))*exp(-((x-#1)^2)/(2*#2^2))}%
}

\begin{frame} 
\maketitle
\end{frame}

\begin{frame}{Second Verse Same(?) as the First}
In this section we will be testing the differences between two proportions, much like we did with testing two means. \newline\\	\pause

Much of the material will be the two-sample version of hypothesis testing of a single proportion.
\end{frame}

\begin{frame}{Test Statistic and $p$-Value}
The test statistic for two sample proportions is given by
\[
t = \frac{(\hat{p}_1-\hat{p}_2) - (p_1 - p_2)}{\sqrt{\frac{\hat{p}_1(1-\hat{p}_1)}{n_1}+\frac{\hat{p}_2(1-\hat{p}_2)}{n_2}}}
\]
where 	\pause
\begin{itemize}
	\item $\hat{p}_1 \text{ and } \hat{p}_2$ represent the sample proportions	\pause
	\item $p_1 \text{ and } p_2$ represent the population proportions	\pause
	\item $n_1 \text{ and } n_2$ represent the sample sizes	\pause
\end{itemize}

The $p$-value is found in the same manner as other sections.
\end{frame}

\begin{frame}{Just For Pools and Giggles}
If using pooled variances, use
\[
\hat{p} = \frac{x_1 + x_2}{n_1 + n_2}
\]
\pause	\newline\\
The test statistic then becomes
\[
t = \frac{(\hat{p}_1-\hat{p}_2) - (p_1 - p_2)}{\sqrt{\hat{p}(1-\hat{p})\left(\frac{1}{n_1} + \frac{1}{n_2}\right)}}
\]
\end{frame}

\begin{frame}{Confidence Intervals}
The $1-\alpha$ confidence interval is calculated as
\[
(\hat{p}_1 - \hat{p}_2) \pm z_{\alpha/2}\sqrt{\frac{\hat{p}_1(1-\hat{p}_1)}{n_1}+\frac{\hat{p}_2(1-\hat{p}_2)}{n_2}}
\]	\pause
Remember, if our confidence interval contains the claimed difference in population proportions, we do not reject the null hypothesis.
\end{frame}

\begin{frame}{You Know What Happens When You Assume, Don't You?}
\textbf{Assumptions for this section}:
\begin{itemize}
	\item<2-> Samples are randomly selected
	\item<3-> Samples are independent
	\item<4-> Each sample size is large enough so that the differences in sampling proportions is approximately normal
	\begin{itemize}
	\item<5-> Good to go if $n_1\hat{p}_1$, $n_1(1-\hat{p}_1)$, $n_2\hat{p}_2$, and $n_2(1-\hat{p}_2)$ are each greater than 5.
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Example 1}
A poll of 450 registered voters is taken and 43\% of them would vote for the incumbent candidate. A week later a poll of 300 different registered voters is taken and 41\% of them would vote for the incumbent candidate. \newline\\

At the $\alpha = 0.05$ significance level, test the claim that the proportions of all registered voters would vote for the incumbent candidate is now different.	\newline\\	\pause

$H_0: \, p_1 = p_2$ \newline	\pause
$H_A: \, p_1 \neq p_2$
\end{frame}

\begin{frame}{Example 1}
Test statistic: $t = 0.544$  (critical value = $\pm 1.96$ \newline \pause
$p$-value: 0.5864 ($\alpha = 0.05$) \newline \pause
95\% Confidence Interval: ($-0.0520$, 0.0920)	\newline\\	\pause
Do Not Reject Null Hypothesis	\pause \newline\\
\begin{quote}
At the 5\% significance level, we do not have sufficient evidence to reject the null hypothesis that the population proportions are the same and conclude that our samples provide evidence that the population proportion of voters are the same.
\end{quote}
\end{frame}

\begin{frame}{Example 2}
According to recent hospital data, 44 out of 145 recent men were hospitalized for heart conditions, while 21 out of 107 women were. At the $\alpha = 0.05$ level of significance, test the claim that the proportion of men admitted for heart conditions is higher than that of women.	\newline\\	\pause

$H_0: \, p_{\text{men}} = p_{\text{women}}$ \newline \pause
$H_A: \, p_{\text{men}} > p_{\text{women}}$
\end{frame}

\begin{frame}{Example 2}
Test statistic: 1.980 (critical value 1.65) \newline \pause
$p$-value: 0.0239 ($\alpha = 0.05$)	\newline \pause
95\% Lower Bound: 0.0181	\newline\\	\pause
Reject the Null Hypothesis	\newline\\	\pause
\begin{quote}
At the 5\% significance level, we have sufficient evidence to reject the claim that the proportion of men and women hospitalized for heart conditions is equal and conclude that our data supports the claim that the proportion of men hospitalized for heart conditions is higher than that of women.
\end{quote}
\end{frame}
\end{document}