\documentclass[t]{beamer}
\usetheme{Copenhagen}
\setbeamertemplate{headline}{} % remove toc from headers
\beamertemplatenavigationsymbolsempty

\usepackage{amsmath, tikz, bm, pgfplots, tcolorbox}
\pgfplotsset{compat = 1.16}

\title{Measures of Center}
\author{}
\date{}

\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Objectives}
    \tableofcontents[currentsection]
  \end{frame}
}

\begin{document}

\begin{frame} 
\maketitle
\end{frame}

\section{Calculate the mean, median, and mode of a dataset}

\begin{frame}{Measures of Center}
In this section, we will look at finding a central location for a dataset. \newline\\	\pause

In some instances, this can give us a good value to expect from that dataset.
\end{frame}

\begin{frame}{The Mean}
\begin{tcolorbox}[colframe=green!20!black, colback = green!30!white,title=\textbf{Mean}]
The \textbf{mean} of a dataset is found by adding all of the data values together and then dividing by the total number of values. 
\end{tcolorbox}
\vspace{11pt}	\pause

When most people use the term \textit{average}, they are referring to the mean.
\end{frame}

\begin{frame}{Properties of the Mean}
\begin{itemize}
	\item<+-> Sample means drawn from the same population tend to vary less than other measures of center.	\newline\\
	\item<+-> The mean of a data set uses every value, unless the mean is a \textit{trimmed mean}.	\newline\\
	\item<+-> One extreme value (called an {\color{blue}\textbf{outlier}}) can change the value of the mean drastically.	\newline\\
\end{itemize}
\end{frame}

\begin{frame}{Mean Formula}
Sample mean: $\overline{x}$	\qquad	Population mean: $\mu$	\newline\\	\pause
\[ \overline{x}, \text{ or } \mu, = \frac{\sum x_i}{n} = \frac{1}{n}\sum x_i	\]
\end{frame}

\begin{frame}{The Median}

\begin{tcolorbox}[colframe=green!20!black, colback = green!30!white,title=\textbf{Median}]
The \textbf{median} of a dataset is found by first arranging the data values from least to greatest, then selecting the data value in the middle. 
\end{tcolorbox}
\vspace{11pt}	\pause

If there are 2 dava values in the middle, the median will be the mean of these two values.
\end{frame}

\begin{frame}{Properties of the Median}
The median separates the top 50\% of the data from the bottom 50\%.	\newline\\	\pause

Unlike, the mean, the median typically does not change by large amounts when we include just a few extreme values; in other words, the median is \textbf{resistant}.	\newline\\	\pause

The median is denoted by $\tilde{x}$, however, some technologies uses \texttt{Med} to denote it.
\end{frame}

\begin{frame}{The Mode}

\begin{tcolorbox}[colframe=green!20!black, colback = green!30!white,title=\textbf{Mode}]
The \textbf{mode} of a dataset is the value(s) that occur the most.
\end{tcolorbox}
\vspace{11pt}	\pause

There may be one mode, no mode, or many modes (2 modes is called \textbf{bimodial}).	\newline\\	\pause

The mode is the only measure of center that is applicable to qualitative data.
\end{frame}

\begin{frame}{Example 1}
The dataset below represents the number of complaints I receive each week about my teaching. \newline\\
\begin{center}
8, 2, 3, 7, 4, 4, 1, 9, 7, 5
\end{center}
\vspace{8pt}

Calculate the mean, median, and mode of the number of complaints.
\end{frame}

\begin{frame}{Example 1}
The total number of complaints is 50. There are 10 complaints listed.	\newline\\	\pause
\begin{center}
Mean = 50/10 = 5 complaints per week.
\end{center}
\vspace{8pt}	\pause

Sorted: 1, 2, 3, 4, 4, 5, 7, 7, 8, 9	\newline\\	\pause
Median number of complaints per week is 4.5	\newline\\	\pause
Mode number of complaints per week are 4 and 7.
\end{frame}

\begin{frame}{Example 2}
The next week, I received 400 complaints. Re-calculate the mean, median, and mode now.	\newline\\	\pause
\begin{center}
1, 2, 3, 4, 4, 5, 7, 7, 8, 9, 400
\end{center}
\vspace{8pt}	\pause

Mean: 450 / 11 = 40.9 complaints per week.	\newline\\	\pause
Median: 5 complaints per week.	\newline\\	\pause
Mode: 4 and 7 complaints per week.
\end{frame}


\section{Calculate the weighted mean of a dataset}

\begin{frame}{Example 3}
California has a mean class size of 20.9 students per teacher and Alaska has a mean of 16.8 students per teacher. \newline\\ 

If we combine the two states, we might find the mean number of students per teacher to be 18.85 (0.5 * (20.9 + 16.8)) but is this result correct? Why or why not?	\newline\\	\pause

It is not correct because California has a much higher population that Alaska. We would have to find what is known as the \textbf{weighted mean}.
\end{frame}

\begin{frame}{Weighted Mean}
Sometimes it is necessary to take into account how large each class of a data set is (such as the population of each US state).	\newline\\	\pause

If $w_i$ represents the {\color{blue}\textbf{weight}} of each class, then the \textbf{weighted mean} can be found via

\[\frac{\sum \left(x_i \cdot w_i\right)}{\sum w_i}\]
\vspace{8pt}	\pause

In other words, \newline\\
\begin{enumerate}
	\item Multiply each data value by its corresponding weight.	\pause
	\item Add those results.	\pause
	\item Then divide that by the total of the weights.
\end{enumerate}
\end{frame}

\begin{frame}{Example 4}
You've recently completed a semester. Determine the semester's GPA (A = 4pts, B = 3pts, etc).	\newline\\
\begin{center}
\begin{tabular}{|c|c|c|}
\textbf{Course} 			&	\textbf{Grade}	&	\textbf{Credit Hours} 	\\	\hline
Statistics					&	A 				&	4						\\
Advanced Chris Farley		&	A 				&	3						\\
\textit{Airplane!} Quotes	&	B 				&	5						\\
Obnoxious Examples			&	C 				&	3						\\
\end{tabular}
\end{center}
\end{frame}

\begin{frame}{Example 4}
\begin{center}
\begin{tabular}{c|c|c}
\textbf{Grade}	&	\textbf{Credit Hours}	&	\textbf{TOTALS} 	\\	\hline
4 				&	4						&	16						\\
4 				&	3						&	12						\\
3 				&	5						&	15						\\
2 				&	3						&	6						\\	\hline
				&	15						&	49					\\
\end{tabular}
\end{center}
\vspace{10pt}	\pause

Weighted Mean: $49/15 = 3.267$
\end{frame}

\begin{frame}{Example 5}
In a statistics course, tests count for 60\% of the final grade, homework for 20\% and midterm and final exams are 10\% each. Suppose you've earned an 87\% average on tests, 94\% average on homeworks and a 77\% average on the exams. \newline\\ 
What is your overall percentage?	\newline\\	\pause
\begin{center}
\begin{tabular}{|c|c|c|c|}
\textbf{Assessment}	&	\textbf{Your Scores}	&	\textbf{Grade Weights}	&	\textbf{TOTALS}	\\	\hline
Tests 				&	0.87					&	0.60					&	0.522			\\
Homework 			&	0.94					&	0.20					&	0.188			\\
Exams 				&	0.77					&	0.20					&	0.154			\\
\end{tabular}
\end{center}
\end{frame}

\begin{frame}{Example 5}
\begin{center}
\begin{tabular}{|c|c|}
\textbf{Grade Weights}	&	\textbf{TOTALS}	\\	\hline
0.60					&	0.522			\\
0.20					&	0.188			\\
0.20					&	0.154			\\	\hline
\onslide<2->{1						&	0.864}			\\
\end{tabular}
\end{center}

Grade: $0.864/1 = 86.4\%$
\end{frame}

\section{Approximate the mean for a grouped dataset}

\end{document}